RadLib: a radiative heat transfer model library for CFD

### 2021-01-01 manuscript/manuscript.tex
initial submission

{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
  %Delete as appropriate.

@@

\section{Conflict of Interest} \label{s:coi}

There are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.

@@

The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb of Brigham Young University for their insights and assistance with the RCSLW model.

>>>>

{\bf PROGRAM SUMMARY}
  %Delete as appropriate.

@@

\section{Declaration of Competing Interes} \label{s:coi}

The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

@@

The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb for their insights and assistance with the RCSLW model. 
This research did not receive any specific grant from funding agencies in the public, commercial, or
not-for-profit sectors.
